---
title: "Proposal title"
subtitle: "Proposal"
author: 
  - name: "Team Name - Team member 1, Team member 2,..."
    affiliations:
      - name: "School of Information, University of Arizona"
description: "Project description"
format:
  html:
    code-tools: true
    code-overflow: wrap
    code-line-numbers: true
    embed-resources: true
    code-fold: true
editor: visual
code-annotations: hover
execute:
  warning: false
---

```{r}
#| label: load-pkgs
#| message: false
library(tidyverse)
if(!require("pacman"))
  install.packages("pacman")

pacman::p_load(tidyverse, gt)


#Ronaldo dataset downloaded from https://www.kaggle.com/datasets/azminetoushikwasi/cr7-cristiano-ronaldo-all-club-goals-stats
ronaldo <- read_csv("data/cr7.csv")


#Messi dataset downloaded from https://www.kaggle.com/code/azminetoushikwasi/lionel-messi-extended-eda-goals/input?select=messi.csv
messi <- read_csv("data/messi.csv")
```

# The Timeless Rivalry: Ronaldo vs Messi

**An investigation tracking Messi and Ronaldo's performance trends**

#### Our High Level Goal

To compare and contrast the performances of Christiano Ronaldo and Lionel Messi, only, over time and space (season / country respectively), via geographical plots primarily

#### First Topic

The first aim is to craft an animation detailing the number of goals scored by both Ronaldo and Messi, plotted geographically over time.

#### Second Topic

The second target is create an interactive map, giving details about a summary of the goals scored in each country by Ronaldo and Messi. It will allow for comparison and contrasting per country between the two players.

#### The Data

The dataset appears to contain information related to football matches, likely from a specific club or league. Here's a breakdown of the columns:

1.  **Season**: Indicates the season of the competition in which the match took place.
2.  **Competition**: Specifies the name or type of the competition (e.g., league, cup).
3.  **Matchday**: Indicates the matchday number within the competition.
4.  **Date**: Represents the date on which the match was played.
5.  **Venue**: Specifies the location where the match was held.
6.  **Club**: Refers to the name of the football club involved in the match.
7.  **Opponent**: Refers to the opposing team.
8.  **Result**: Indicates the outcome of the match, usually in terms of goals scored by each team.
9.  **Playing_Position**: Specifies the position played by the player.
10. **Minute**: Indicates the minute in which a particular event occurred (e.g., goal, substitution).
11. **At_score**: Represents the score at the time of the event.
12. **Type**: Describes the type of event (e.g., goal, assist).
13. **Goal_assist**: Indicates the player who assisted in scoring the goal.

Concurrently, here's the table with only the datatype and a brief description of each column:

| Column Name      | Datatype | Description                                 |
|------------------|----------|---------------------------------------------|
| Season           | Object   | Season of the competition                   |
| Competition      | Object   | Type of the competition                     |
| Matchday         | Integer  | Matchday number within the competition      |
| Date             | Object   | Date of the match                           |
| Venue            | Object   | Location where the match was held           |
| Club             | Object   | Name of the football club                   |
| Opponent         | Object   | Name of the opposing team                   |
| Result           | Object   | Outcome of the match                        |
| Playing_Position | Object   | Position played by the player               |
| Minute           | Object   | Minute in which a particular event occurred |
| At_score         | Object   | Score at the time of the event              |
| Type             | Object   | Type of event                               |
| Goal_assist      | Object   | Player who assisted in scoring the goal     |

```{r}
ronaldoTop <- head(ronaldo)
messiTop <- head(messi)


ronaldoTop %>%gt() %>%
tab_header(title = "Christiano Ronaldo") %>%
  
tab_style(
  style = list(cell_fill(color = "#fff0ef"),
  cell_text(weight = "bold")),
locations = cells_body(columns = Competition)) %>% 
  
tab_style(
  style = cell_text(weight = "bold"),
  locations = cells_column_labels()
)



messiTop %>%gt() %>%
tab_header(title = "Lionel Messi") %>%
  
tab_style(
  style = list(cell_fill(color = "#b2f7ef"),
  cell_text(weight = "bold")),
locations = cells_body(columns = Competition)) %>% 
  
tab_style(
  style = cell_text(weight = "bold"),
  locations = cells_column_labels()
)

```

#### Our Weekly Plan

| Task Name                  | Status  | Assignee | Due      | Priority | Summary                                          |
|----------------------------|---------|----------|----------|----------|--------------------------------------------------|
| Create the proposal        | Pending |          | 03 April | High     | Create the initial documented proposal           |
| Create the Git Repo        | Pending |          | 03 April | Moderate | Create a new repository for data                 |
| Resubmit proposal          | Pending |          | 08 April | High     | Resubmit revised proposal                        |
| Data wrangling             | Pending |          | 08 April | Moderate | Initial exploration and cleaning of the datasets |
| Analysis of topic one      | Pending |          | 15 April | Moderate |                                                  |
| Analysis of topic two      | Pending |          | 22 April | Low      |                                                  |
| Plotting for topic one     | Pending |          | 29 April | Low      |                                                  |
| Plotting for topic two     | Pending |          | 29 April | Low      |                                                  |
| Summarising of information | Pending |          | 01 May   | Low      |                                                  |
| Write up                   | Pending |          | 06 May   | Low      |                                                  |
| Presentation               | Pending |          | 06 May   | Low      |                                                  |
| Final organisation         | Pending |          | 06 May   | Low      |                                                  |
| Site publishing            | Pending |          | 06 May   | Low      |                                                  |
| Final submission           | Pending |          | 06 May   | Low      | Final submission of the entire repository        |
